# mapDK

```{r global_options, include = FALSE}
library(knitr)
options(width = 120)
opts_chunk$set(fig.width = 12, fig.height = 8, fig.path = 'figure/',
               include = TRUE, warning = FALSE, message = FALSE)
```

This is a very incomplete draft of a mapDK package for making easy ggplot2 based maps of Denmark.

Currently, the package allows you to do two things:

1. make basic maps of DK at the municipality or parish level
2. turn these maps into (static) chloropleth maps

I will make it possible to create interactive chloropleth maps when R's interactive libraries such as rCharts, leaftletR, or ggvis, matures a little. 

To install the package simply run

```{r}
devtools::install_github("sebastianbarfort/mapDK")
````

To use the basic maps simply run 

```{r}
library(mapDK)
mapDK()
````

The default plot is one of Denmark's 98 municipalities. You can plot Denmark at the parish level by adding `detail = "parish"` in the `mapDK` call

```{r}
mapDK(detail = "parish")
````

To create a static chloropleth map I've added some test data to the package. 

We can create a map by simply specifying the values and id's (as strings) and the dataset in the call to `mapDK`

```{r}
mapDK(values = "indbrud", id = "kommune", data = test.data)
````

If you don't provide names for all municipalities (or parishes), the function will throw a warning. Let's randomly remove 20 rows and plot the data again

```{r}
test.data.2 = mapDK::test.data[-sample(1:nrow(mapDK::test.data), 20), ]
mapDK(values = "indbrud", id = "kommune", data = test.data.2)
```

You can remove missing municipalities by changing `show_missing` to false

```{r}
mapDK(values = "indbrud", id = "kommune", data = test.data.2, show_missing = FALSE)
```

You can also provide a `sub` option specifying what municipalities in your data you want plotted

```{r}
mapDK(values = "indbrud", id = "kommune", data = test.data, sub = c("Viborg", "Esbjerg"))
```




